---
title: "naive Bayes"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Naive Bayes Classifier
```{r}
library(e1071)
library(mlbench)
library(randomForest)
```
## Problem to solve
## there are 6 types of glasses

## based on 9 elements, to predict which type
## out of 6

## load data set
```{r}
data(Glass)
head(Glass, 3)
```

## split data to : train and test
```{r}
set.seed(2022)
n = nrow(Glass)
train_index <- sample(n, floor(0.7 * n))
```
## convert Species into factor

```{r}
iris$Species <- as.factor(iris$Species)
```

## create train and test data
```{r}
train_data <- Glass[train_index, ]
test_data <- Glass[-train_index, ]
```

## build the Naive Baye model
```{r}
nb_classifier <- naiveBayes(Type ~., data = train_data)
```

## make predictions on test data
```{r}
pred <- predict(nb_classifier, newdata = test_data)
```

## evaluate the prediction accuracy
```{r}
table(test_data$Type, pred)
```

```{r}
(1 + 0 + 5 + 4 + 0 + 3) / nrow(test_data)
```

## build the random forest model
```{r}
rf_classifier <- randomForest(Type ~., data = train_data)
```

## make predictions on test data
```{r}
pred <- predict(rf_classifier, newdata = test_data)
```

## evaluate the prediction accuracy
```{r}
table(test_data$Type, pred)
```

```{r}
# accuracy
(20 + 20 + 1 + 4 + 1 + 5) / nrow(test_data)
```
## build a LDA model

```{r}
library(MASS)
```

```{r}
lda_classifier <- lda(Type ~., data = train_data)
```

## make predictions on test data
```{r}
pred <- predict(lda_classifier, newdata = test_data)
```

## evaluate the prediction accuracy
```{r}
table(test_data$Type, pred$class)
```

```{r}
# accuracy
(16 + 14 + 0 + 4 + 0 + 5) / nrow(test_data)
```

