---
title: "Chapter 27 R Markdown"
output: html_document
params:
  my_class: "suv"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
class <- mpg %>% filter(class == params$my_class)


smaller <- diamonds %>% 
  filter(carat <= 2.5)
```
We have data about `r nrow(diamonds)` diamonds. Only 
`r nrow(diamonds) - nrow(smaller)` are larger than
2.5 carats. The distribution of the remainder is shown
below:

```{r plot, echo = FALSE}
smaller %>% 
  ggplot(aes(carat)) + 
  geom_freqpoly(binwidth = 0.01)
```

## text formatting with markdown
### table
```{r}
mtcars[1:5, ]
```
```{r}
knitr::kable(
  mtcars[1:5, ],
  caption = "A knitr kable"
)
```
### caching
{r processed_data, cache = TRUE, dependson = "raw_data"}

### global options
### inline code
```{r}
comma <- function(x) format(x, digits = 2, big.mark = ",")
comma(3452345)
comma(0.12345678)
```
## trouble shooting
*The most common difference is the working directory: the working directory of an R Markdown is the directory in which it lives. Check the working directory is what you expect by including getwd() in a chunk.*

## YAML header
### parameters

Fuel economy for `r params$my_class`s

```{r, message = FALSE}
ggplot(class, aes(displ, hwy)) + 
  geom_point() + 
  geom_smooth(se = FALSE)
```
### bibliographies and citations

